Reconstructing Rearrangement Phylogenies

### 2023-10-19 docs/manuscript/main.tex
add comment w.r.t. matchings
Add some initial commands

\documentclass{article}[7pt]
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\include{ilputil}
\title{spp-dcj-cf}
\author{lbohnenk }
\date{June 2023}
\usepackage{algorithm}
\usepackage{placeins}
\usepackage{bbm}
\begin{document}
\newcommand{\extremityedges}{E_{ext}}
\newcommand{\adjacencyedges}{E_{adj}}
\newcommand{\indeledges}{E_{id}}
\newcommand{\idx}[1]{\texttt{ix}(#1)}
\newcommand{\parityvar}{b}
\newcommand{\caps}{V_{\varnothing}}
\newcommand{\trans}{|}
\newcommand{\cis}{\circ}
\newcommand{\coolone}{\mathbbm{1}}

\begin{algorithm}[htb]
\caption{new ILP}
\textbf{Minimize:}
\begin{equation*}
    n - c -q
\end{equation*}

\begin{constraints}

\begin{tabular}{lcl}
    \cns & $x_{e} = 1 $ & $\forall e\in \adjacencyedges$\\
     \cns & $\sum_{uv\in E_{ext} \cup E_{id} } x_{uv}= 1$ & $\forall u\in V\setminus V_{\varnothing}$  \\
     \cns & $x_e=x_d$ & for all sibling edges $e,d$\\
     \cns & $y_v + \idx{u}(1-x_{uv}) \geq y_u$ &$\forall uv \in \adjacencyedges\cup \extremityedges$\\
          & $\idx{u}(1-x_{uv})\geq y_u$& $\forall uv \in \indeledges$\\
    \cns & $\idx{v}z_v \leq y_v$ & $\forall v\in V $\\
    \cns & matching condition\\
    \cns & $\parityvar_v = \coolone_{v \text{ of genome } B}$ & $\forall v \in \caps$\\
    \cns & $\parityvar_v \leq 1 - x_{uv}$ & $\forall uv \in \indeledges \text{ of genome } A$\\
     & $\parityvar_v \geq  x_{uv}$ & $\forall uv \in \indeledges \text{ of genome } B$\\
    \cns & $\parityvar_v \leq \parityvar_u +  x_{uv}$& $\forall uv \in \extremityedges$\\
    & $\parityvar_u \leq \parityvar_v + r_{uv}^{a\trans b} + (1-x_{uv})$& $\forall uv\in E_{adj},u,v\notin \caps$\\
    & $\parityvar_u \leq \parityvar_v + r_{uv}^{A\trans B} + r_{uv}^{A\trans b} + (1-x_{uv})$& $\forall uv\in E_{adj}, u \text{ or } v\in \caps^A$\\
    & $\parityvar_u \leq \parityvar_v + r_{uv}^{B\trans a} + (1-x_{uv})$& $\forall uv\in E_{adj}, u \text{ or } v\in \caps^B$\\
    \cns & $a_v = 0$ & $\forall v\in V_{\varnothing}$\\
    \cns & $x_{uv} \leq a_v$&$\forall uv\in E_{id}$\\
    \cns & $a_v \leq a_u + (1-x_{uv})$&$\forall uv\in E_{ext}$\\
    \cns & $a_v \leq a_u + r_{uv}^{A\trans b} + r_{uv}^{A\cis a}$&$\forall uv\in E_{adj}, u \text{ or } v\in \caps^A$\\
    & $a_v \leq a_u + r_{uv}^{B\trans a} + r_{uv}^{B\cis b}$&$\forall uv\in E_{adj}, u \text{ or } v\in \caps^B$\\
    \cns & $r_{uv}^c + r_{uv}^{A\trans B} \leq z_v + z_u$&$\forall uv \in E_{adj}$\\
    \cns & $r_{uv}^{R} \leq b_u + b_v$\\
    \cns & $r_{uv}^{R} \leq 2-b_u - b_v$&$\forall R \in \{A\trans B, A\trans b, B\trans a\}$\\
    \cns & $r_{uv}^{a\trans b} \leq x_{uw} + x_{vz}$&$\forall uv\in E_{adj}, uw,vz \in E_{ide}$\\
    \cns & $(u+v)(1-r_{uv}^{P}) \geq y_u +y_v$&$R\in  \{A\trans b , B\trans a , a\trans b, A\cis a , B\cis b\}$\\
    \cns & $ r_{uv}^{c\cis}\leq a_v + a_u $\\

    \cns & $n = 0.5 \sum_{e \in E_{ext}} x_{e}$\\
    \cns & $c = \sum_{uv\in E_{adj}} r^c_{uv}$\\
    \cns & $2q \geq p^{a\trans b}+ p^{ABa} + p^{ABb} - p^{A\trans B} $\\
    \cns & $p^{a\trans b} = \sum_{uv \in E_{adj}}r^{a\trans b}_{uv}$\\
    \cns & $p^{A\trans b} = \sum_{uv \in E_{adj}} r^{A\trans b}$\\
    \cns & $p^{B\trans a} = \sum_{uv \in E_{adj}} r^{B\trans a}$\\
    \cns & $p^{A\cis a} = \sum_{uv \in E_{adj}} r^{A\cis a}$\\
    \cns & $p^{B\cis b} = \sum_{uv \in E_{adj}} r^{B\cis b}$\\
    \cns & $p^{ABa} \geq p^{B\trans a}$\\
    \cns & $p^{ABa} \geq p^{A\cis a}$\\
    \cns & $p^{ABb} \geq p^{B\cis b}$\\
    \cns & $p^{ABb} \geq p^{A\trans b}$\\
    \cns & $p^{A\trans B} = \sum_{uv\in E_{adj}} r^{A\trans B}$\\
    \cns\cns & Circ sing\\
    \cns & $r^{c}_{uv} \leq x_{uv}$& only for spp-DCJ\\
\end{tabular}
\end{constraints}

\end{algorithm}
\end{document}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\input{preamble}
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:

%\renewcommand\UrlFont{\color{blue}\rmfamily}
%

\begin{document}
%
\title{Reconstructing Rearrangement Phylogenies}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%

\section{Introduction}
\section{Background}
\subsection{Problem Formulation}
\section{A new Method}
\subsection{Pre-selecting Adjacencies}
\todoDany{Describe Process}
\subsection{A New ILP Formulation}
\todoLeo{ILP goes here}

\section{Evaluation}
\section{Discussion}

\nocite{DOE-CHA-2021}
\nocite{BOH-BRA-DOE-STO-2021}
\subsubsection{Acknowledgements} Please place your acknowledgments at
the end of the paper, preceded by an unnumbered run-in heading (i.e.
3rd-level heading).

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{refs}

\end{document}
